Observations

### 2020-04-27 exp_eth_val.Rmd
experiment on 270420
all experiments to select

wd <- setwd("C:/Users/rocpa/OneDrive/Desktop/AF/")
dataone <- read.csv("experiments/80_50_onebeta.csv",sep = ";",skip = 1)

@@

maj_val <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= val_seg)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) + 
  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

@@

@@

majority

@@

```{r testnorm, echo=FALSE, include= FALSE}

nrml <- function(mx,mn,x,s){

@@

 bt_10 <- for (x in seq(5,10,by=1)) {

  mx <- 10
  mn <- 5

  s <- nrml(mx,mn,x,s)
  print(c(x,s))

@@

  s <- nrml(mx,mn,x,s)
  print(c(x,s))

>>>>

wd <- setwd("C:/Users/rocpa/OneDrive/Desktop/AF/")
dataone <- read.csv("experiments/80_50_onebeta.csv",sep = ";",skip = 1)
datatwo <- read.csv("experiments/two_beta.csv", sep = ";",skip = 1)

@@

maj_val <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= val_seg)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) + 
  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
 scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
maj_val

@@

```{r betatwoethnic,out.width="96%", fig.pos="t",fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="Difference segregation between value groups (equal ethnic group). X-axis: determinism ethnic utility circle.", echo=FALSE, include=TRUE }

circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_iv_circle == 0 |beta_iv_circle == 5 |beta_iv_circle == 10 ) %>% filter(beta_ie_circle == 0 | beta_ie_circle == 5 | beta_ie_circle == 10)

 v_circle.labs <- c("ß value circle 0", "ß value circle 5", "ß value circle 10")
names(v_circle.labs) <- c("0", "5","10")
e_circle.labs <- c("ß ethnic circle 0", "ß ethnic circle 5", "ß ethnic circle 10")
names(e_circle.labs) <- c("0", "5","10")

ie_10 <- circle_frame %>%  filter(beta_ie_square == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority"))) %>%
  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(beta_iv_circle ~  beta_ie_circle, labeller = labeller(beta_iv_circle = v_circle.labs,  beta_ie_circle = e_circle.labs )) +
  geom_vline(xintercept = 5, color = "red") +
  scale_x_discrete(name = "ß ethnic square 10 - ß value square", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ie_5 <- circle_frame %>%  filter(beta_ie_square == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority"))) %>%
  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(beta_iv_circle ~  beta_ie_circle, labeller = labeller(beta_iv_circle = v_circle.labs,  beta_ie_circle = e_circle.labs )) +
  scale_x_discrete(name = "ß ethnic square 5 - ß value square", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ie_5
ie_10
```

```{r betatwovalue, out.width="96%", fig.pos="t",fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="Difference segregation between value groups (equal ethnic group). X-axis: determinism value utility circle.", echo=FALSE, include=TRUE  }

circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_ie_square == 0 |beta_ie_square == 5 |beta_ie_square == 10 ) %>% filter(beta_iv_square == 0 | beta_iv_square == 5 | beta_iv_square == 10)

e_square.labs <- c("ß ethnic \nsquare 0", "ß ethnic \nsquare 5", "ß ethnic \nsquare 10")
names(e_square.labs) <- c("0", "5","10")
v_square.labs <- c("ß value square 0", "ß value square 5", "ß value square 10")
names(v_square.labs) <- c("0", "5","10")

iv_10 <- circle_frame %>%  filter(beta_iv_circle == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority")))  %>%
  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(beta_ie_square ~  beta_iv_square, labeller = labeller(beta_ie_square = e_square.labs, beta_iv_square = v_square.labs))  +
  geom_vline(xintercept = 5, color = "red") +
  scale_x_discrete(name = "ß value circle 10 - ß ethnic circle", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

iv_5 <- circle_frame %>%  filter(beta_iv_circle == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority")))  %>%
  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(beta_ie_square ~  beta_iv_square, labeller = labeller(beta_ie_square = e_square.labs, beta_iv_square = v_square.labs))  +
  scale_x_discrete(name = "ß value circle 5 - ß ethnic circle", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

iv_5
iv_10

@@

@@

<!--
```{r testnormdelete, echo=FALSE, include= FALSE}

nrml <- function(mx,mn,x){

@@

 bt_10 <- for (x in seq(0,5,by=1)) {

  s <- nrml(mx,mn,x)
  print(c(x,s))

@@

  s <- nrml(mx,mn,x)
  print(c(x,s))
